Computing astrophysical inferences with diffusive nested sampling

### 2014-03-07 ms.tex
Why dnest is godo

A multi-threaded, free software C++ implementation of Diffusive Nested Sampling
is available online at {\tt http://github.com/eggplantbren/DNest3}.

\section{Probabilistic Catalogs}
Many questions in astronomy can be classified as ``source detection'' problems.
Telescopes (whether optical, radio, or whatever) obtain some data, and we would
like to use this data to infer the presence and properties of the objects in
that part of the sky. Several different techniques and software packages have
been developed for carrying this out \citep[e.g.][]{sextractor, dolphot}.
However, this process
can also be described as a Bayesian inference problem \citep{starfield}.
The hypothesis space is the set of possible answers to the question
``how many objects are there, and what are their properties (positions, fluxes,
etc)''. The prior

@@

>>>>

A key advantage of DNS over standard MCMC-based Nested Sampling is the performance
on multimodal distributions. With DNS, if two particles are in two separate
but identical modes, there is no need for any deleting or copying of particles.
The two particles will simply continue exploring their own modes. A particle is
only deleted if it is unable to keep up with the bulk of the other particles.
This way, the diversity created by having multiple starting points is maintained
for as long as possible. A multi-threaded, free software C++ implementation of
DNS, called {\tt DNest3},
is available online at {\tt http://github.com/eggplantbren/DNest3}.

\section{Probabilistic Catalogs}
Many questions in astronomy can be classified as ``source detection'' problems.
Telescopes (whether optical, radio, or whatever) obtain some data, and we would
like to use this data to infer the presence and properties of the objects in
that part of the sky. Several different techniques and software packages have
been developed for carrying this out \citep[e.g.][]{sextractor, dolphot}.
However, this process
can also be described as a Bayesian inference problem \citep{starfield}.
The hypothesis space is the set of possible answers to the question
``how many objects are there, and what are their properties (positions, fluxes,
etc)''. This problem has been addressed from a Bayesian point of view by several
authors \citep[e.g.][]{2003MNRAS.338..765H}.

@@

\bibitem[Hobson 
\& McLachlan(2003)]{2003MNRAS.338..765H} Hobson, M.~P., \& McLachlan, C.\ 2003, Monthly Notices of the Royal Astronomical Society, 338, 765
